\begingroup
\small
\sloppy
\begin{enumerate}[leftmargin=2em, itemsep=0.3em, topsep=0.4em, parsep=0pt]
    \item Kara-Ali Aliev, Artem Sevastopolsky, Maria Kolos, Dmitry Ulyanov, and Victor Lempitsky. 2020. Neural Point-Based Graphics. In \textit{Computer Vision -- ECCV 2020: 16th European Conference, Glasgow, UK, August 23--28, 2020, Proceedings, Part XXII}. 696--712.

    \item Jonathan T. Barron, Ben Mildenhall, Matthew Tancik, Peter Hedman, Ricardo Martin-Brualla, and Pratul P. Srinivasan. 2021. Mip-NeRF: A multiscale representation for anti-aliasing neural radiance fields. In \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision}. 5855--5864.

    \item Jonathan T. Barron, Ben Mildenhall, Dor Verbin, Pratul P. Srinivasan, and Peter Hedman. 2022. Mip-NeRF 360: Unbounded Anti-Aliased Neural Radiance Fields. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}.

    \item Sebastien Bonopera, Jerome Esnault, Siddhant Prakash, Simon Rodriguez, Theo Thonat, Mehdi Benadel, Gaurav Chaurasia, Julien Philip, and George Drettakis. 2020. SIBR: A System for Image Based Rendering. \url{https://gitlab.inria.fr/sibr/sibr_core}.

    \item Mario Botsch, Alexander Hornung, Matthias Zwicker, and Leif Kobbelt. 2005. High-Quality Surface Splatting on Today's GPUs. In \textit{Proceedings of the Second Eurographics / IEEE VGTC Conference on Point-Based Graphics (SPBG '05)}. Eurographics Association, Goslar, DEU, 17--24.

    \item Chris Buehler, Michael Bosse, Leonard McMillan, Steven Gortler, and Michael Cohen. 2001. Unstructured lumigraph rendering. In \textit{Proceedings of SIGGRAPH}.

    \item Gaurav Chaurasia, Sylvain Duchene, Olga Sorkine-Hornung, and George Drettakis. 2013. Depth synthesis and local warps for plausible image-based navigation. \textit{ACM Transactions on Graphics (TOG)} 32, 3 (2013), 1--12.

    \item Anpei Chen, Zexiang Xu, Andreas Geiger, Jingyi Yu, and Hao Su. 2022b. TensoRF: Tensorial Radiance Fields. In \textit{European Conference on Computer Vision (ECCV)}.

    \item Zhiqin Chen, Thomas Funkhouser, Peter Hedman, and Andrea Tagliasacchi. 2022a. MobileNeRF: Exploiting the Polygon Rasterization Pipeline for Efficient Neural Field Rendering on Mobile Architectures. \textit{arXiv preprint arXiv:2208.00277} (2022).

    \item Ricardo L. de Queiroz and Philip A. Chou. 2016. Compression of 3D point clouds using a region-adaptive hierarchical transform. \textit{IEEE Transactions on Image Processing} 25, 8 (2016), 3947--3956.

    \item Martin Eisemann, Bert De Decker, Marcus Magnor, Philippe Bekaert, Edilson de Aguiar, Naveed Ahmed, Christian Theobalt, and Anita Sellent. 2008. Floating textures. In \textit{Computer Graphics Forum}, Vol. 27. Wiley Online Library, 409--418.

    \item John Flynn, Ivan Neulander, James Philbin, and Noah Snavely. 2016. DeepStereo: Learning to predict new views from the world's imagery. In \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition}.

    \item Alex Fridovich-Keil, Matthew Tancik, Qinhong Chen, Benjamin Recht, and Angjoo Kanazawa. 2022. Plenoxels: Radiance Fields without Neural Networks. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}.

    \item Stephan J. Garbin, Marek Kowalski, Matthew Johnson, Jamie Shotton, and Julien Valentin. 2021. FastNeRF: High-Fidelity Neural Rendering at 200FPS. In \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV)}. 14346--14355.

    \item Michael Goesele, Noah Snavely, Brian Curless, Hugues Hoppe, and Steven M. Seitz. 2007. Multi-view stereo for community photo collections. In \textit{Proceedings of the IEEE International Conference on Computer Vision}.

    \item Steven J. Gortler, Radek Grzeszczuk, Richard Szeliski, and Michael F. Cohen. 1996. The lumigraph. In \textit{Proceedings of the 23rd Annual Conference on Computer Graphics and Interactive Techniques}. 43--54.

    \item Markus Gross and Hanspeter Pfister (Eds.). 2011. \textit{Point-Based Graphics}. Elsevier.

    \item Jeff P. Grossman and William J. Dally. 1998. Point Sample Rendering. In \textit{Rendering Techniques}.

    \item Peter Hedman, Julien Philip, True Price, Jan-Michael Frahm, George Drettakis, and Gabriel Brostow. 2018. Deep blending for free-viewpoint image-based rendering. \textit{ACM Transactions on Graphics (TOG)} 37, 6 (2018).

    \item Peter Hedman, Tobias Ritschel, George Drettakis, and Gabriel Brostow. 2016. Scalable Inside-Out Image-Based Rendering. \textit{ACM Transactions on Graphics (SIGGRAPH Asia Conference Proceedings)} 35, 6 (December 2016). \url{http://www-sop.inria.fr/reves/Basilic/2016/HRDB16}.

    \item Peter Hedman, Pratul P. Srinivasan, Ben Mildenhall, Jonathan T. Barron, and Paul Debevec. 2021. Baking Neural Radiance Fields for Real-Time View Synthesis. In \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision}.

    \item Philipp Henzler, Niloy J. Mitra, and Tobias Ritschel. 2019. Escaping Plato's cave: 3D shape from adversarial rendering. In \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision}. 9984--9993.

    \item Arno Knapitsch, Jaesik Park, Qian-Yi Zhou, and Vladlen Koltun. 2017. Tanks and Temples: Benchmarking large-scale scene reconstruction. \textit{ACM Transactions on Graphics (TOG)} 36, 4 (2017), 1--13.

    \item Georgios Kopanas, Thomas Leimk{\"u}hler, Gilles Rainer, Cl{\'e}ment Jambon, and George Drettakis. 2022. Neural Point Catacaustics for Novel-View Synthesis of Reflections. \textit{ACM Transactions on Graphics (SIGGRAPH Asia Conference Proceedings)} 41, 6 (2022), 201. \url{http://www-sop.inria.fr/reves/Basilic/2022/KLRJD22}.

    \item Georgios Kopanas, Julien Philip, Thomas Leimk{\"u}hler, and George Drettakis. 2021. Point-Based Neural Rendering with Per-View Optimization. \textit{Computer Graphics Forum} 40, 4 (2021), 29--43. \url{https://doi.org/10.1111/cgf.14339}.

    \item Samuli Laine and Tero Karras. 2011. High-performance software rasterization on GPUs. In \textit{Proceedings of the ACM SIGGRAPH Symposium on High Performance Graphics}. 79--88.

    \item Christoph Lassner and Michael Zollh{\"o}fer. 2021. Pulsar: Efficient Sphere-Based Neural Rendering. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}. 1440--1449.

    \item Marc Levoy and Pat Hanrahan. 1996. Light field rendering. In \textit{Proceedings of the 23rd Annual Conference on Computer Graphics and Interactive Techniques}. 31--42.

    \item Stephen Lombardi, Tomas Simon, Gabriel Schwartz, Michael Zollh{\"o}fer, Yaser Sheikh, and Jason Saragih. 2021. Mixture of volumetric primitives for efficient neural rendering. \textit{ACM Transactions on Graphics (TOG)} 40, 4 (2021), 1--13.

    \item Duane G. Merrill and Andrew S. Grimshaw. 2010. Revisiting sorting for GPGPU stream architectures. In \textit{Proceedings of the 19th International Conference on Parallel Architectures and Compilation Techniques}. 545--546.

    \item Ben Mildenhall, Pratul P. Srinivasan, Matthew Tancik, Jonathan T. Barron, Ravi Ramamoorthi, and Ren Ng. 2020. NeRF: Representing Scenes as Neural Radiance Fields for View Synthesis. In \textit{European Conference on Computer Vision (ECCV)}.

    \item Thomas M{\"u}ller, Alex Evans, Christoph Schied, and Alexander Keller. 2022. Instant Neural Graphics Primitives with a Multiresolution Hash Encoding. \textit{ACM Transactions on Graphics} 41, 4, Article 102 (July 2022), 15 pages. \url{https://doi.org/10.1145/3528223.3530127}.

    \item Eric Penner and Li Zhang. 2017. Soft 3D reconstruction for view synthesis. \textit{ACM Transactions on Graphics (TOG)} 36, 6 (2017), 1--11.

    \item Hanspeter Pfister, Matthias Zwicker, Jeroen van Baar, and Markus Gross. 2000. Surfels: Surface Elements as Rendering Primitives. In \textit{Proceedings of the 27th Annual Conference on Computer Graphics and Interactive Techniques (SIGGRAPH '00)}. ACM Press/Addison-Wesley Publishing Co., USA, 335--342. \url{https://doi.org/10.1145/344779.344936}.

    \item Christian Reiser, Songyou Peng, Yiyi Liao, and Andreas Geiger. 2021. KiloNeRF: Speeding up Neural Radiance Fields with Thousands of Tiny MLPs. In \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV)}.

    \item Liu Ren, Hanspeter Pfister, and Matthias Zwicker. 2002. Object Space EWA Surface Splatting: A Hardware Accelerated Approach to High Quality Point Rendering. \textit{Computer Graphics Forum} 21 (2002).

    \item Helge Rhodin, Nadia Robertini, Christian Richardt, Hans-Peter Seidel, and Christian Theobalt. 2015. A versatile scene model with differentiable visibility applied to generative pose estimation. In \textit{Proceedings of the IEEE International Conference on Computer Vision}. 765--773.

    \item Gernot Riegler and Vladlen Koltun. 2020. Free view synthesis. In \textit{European Conference on Computer Vision}. Springer, 623--640.

    \item Darius R{\"u}ckert, Linus Franke, and Marc Stamminger. 2022. ADOP: Approximate Differentiable One-Pixel Point Rendering. \textit{ACM Transactions on Graphics} 41, 4, Article 99 (Jul 2022), 14 pages. \url{https://doi.org/10.1145/3528223.3530122}.

    \item Miguel Sainz and Renato Pajarola. 2004. Point-based rendering techniques. \textit{Computers and Graphics} 28, 6 (2004), 869--879. \url{https://doi.org/10.1016/j.cag.2004.08.014}.

    \item Johannes Lutz Sch{\"o}nberger and Jan-Michael Frahm. 2016. Structure-from-Motion Revisited. In \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}.

    \item Markus Sch{\"u}tz, Bernhard Kerbl, and Michael Wimmer. 2022. Software Rasterization of 2 Billion Points in Real Time. \textit{Proceedings of the ACM on Computer Graphics and Interactive Techniques} 5, 3, Article 24 (Jul 2022), 17 pages. \url{https://doi.org/10.1145/3543863}.

    \item Vincent Sitzmann, Justus Thies, Felix Heide, Matthias Nie{\ss}ner, Gordon Wetzstein, and Michael Zollh{\"o}fer. 2019. DeepVoxels: Learning persistent 3D feature embeddings. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}. 2437--2446.

    \item Noah Snavely, Steven M. Seitz, and Richard Szeliski. 2006. Photo tourism: exploring photo collections in 3D. In \textit{Proceedings of SIGGRAPH}.

    \item Carsten Stoll, Nils Hasler, Juergen Gall, Hans-Peter Seidel, and Christian Theobalt. 2011. Fast articulated motion tracking using a sums of gaussians body model. In \textit{2011 International Conference on Computer Vision}. IEEE, 951--958.

    \item Cheng Sun, Min Sun, and Hwann-Tzong Chen. 2022. Direct Voxel Grid Optimization: Super-fast Convergence for Radiance Fields Reconstruction. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}.

    \item Towaki Takikawa, Alex Evans, Jonathan Tremblay, Thomas M{\"u}ller, Morgan McGuire, Alec Jacobson, and Sanja Fidler. 2022. Variable bitrate neural fields. In \textit{ACM SIGGRAPH 2022 Conference Proceedings}. 1--9.

    \item Towaki Takikawa, Joey Litalien, Kangxue Yin, Karsten Kreis, Charles Loop, Derek Nowrouzezahrai, Alec Jacobson, Morgan McGuire, and Sanja Fidler. 2021. Neural Geometric Level of Detail: Real-time Rendering with Implicit 3D Shapes. 2021.

    \item Ayush Tewari, Justus Thies, Ben Mildenhall, Pratul Srinivasan, Edgar Tretschk, Yifan Weng, Christoph Lassner, Vincent Sitzmann, Ricardo Martin-Brualla, Stephen Lombardi, et al. 2022. Advances in neural rendering. In \textit{Computer Graphics Forum}, Vol. 41. Wiley Online Library, 703--735.

    \item Justus Thies, Michael Zollh{\"o}fer, and Matthias Nie{\ss}ner. 2019. Deferred neural rendering: Image synthesis using neural textures. \textit{ACM Transactions on Graphics (TOG)} 38, 4 (2019), 1--12.

    \item Angtian Wang, Peng Wang, Jian Sun, Adam Kortylewski, and Alan Yuille. 2023. VoGE: A Differentiable Volume Renderer using Gaussian Ellipsoids for Analysis-by-Synthesis. In \textit{The Eleventh International Conference on Learning Representations}.

    \item Olivia Wiles, Georgia Gkioxari, Richard Szeliski, and Justin Johnson. 2020. SynSin: End-to-end view synthesis from a single image. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}. 7467--7477.

    \item Xiuchao Wu, Jiamin Xu, Zihan Zhu, Hujun Bao, Qixing Huang, James Tompkin, and Weiwei Xu. 2022. Scalable Neural Indoor Scene Rendering. \textit{ACM Transactions on Graphics (TOG)} (2022).

    \item Yiheng Xie, Towaki Takikawa, Shunsuke Saito, Or Litany, Shiqin Yan, Numair Khan, Federico Tombari, James Tompkin, Vincent Sitzmann, and Srinath Sridhar. 2022. Neural fields in visual computing and beyond. In \textit{Computer Graphics Forum}, Vol. 41. Wiley Online Library, 641--676.

    \item Qiangeng Xu, Zexiang Xu, Julien Philip, Sai Bi, Zhixin Shu, Kalyan Sunkavalli, and Ulrich Neumann. 2022. Point-NeRF: Point-based neural radiance fields. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}. 5438--5448.

    \item Yifan Wang, Felice Serena, Shihao Wu, Cengiz {\"O}ztireli, and Olga Sorkine-Hornung. 2019. Differentiable surface splatting for point-based geometry processing. \textit{ACM Transactions on Graphics (TOG)} 38, 6 (2019), 1--14.

    \item Alex Yu, Ruilong Li, Matthew Tancik, Hao Li, Ren Ng, and Angjoo Kanazawa. 2021. PlenOctrees for Real-time Rendering of Neural Radiance Fields. In \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision}.

    \item Qiang Zhang, Seung-Hwan Baek, Szymon Rusinkiewicz, and Felix Heide. 2022. Differentiable Point-Based Radiance Fields for Efficient View Synthesis. In \textit{SIGGRAPH Asia 2022 Conference Papers (SA '22)}. Association for Computing Machinery, New York, NY, USA, Article 7, 12 pages. \url{https://doi.org/10.1145/3550469.3555413}.

    \item Tinghui Zhou, Shubham Tulsiani, Weilun Sun, Jitendra Malik, and Alexei A. Efros. 2016. View synthesis by appearance flow. In \textit{European Conference on Computer Vision}. Springer, 286--301.

    \item Matthias Zwicker, Hanspeter Pfister, Jeroen van Baar, and Markus Gross. 2001a. EWA volume splatting. In \textit{Proceedings Visualization, 2001. VIS '01}. IEEE, 29--538.

    \item Matthias Zwicker, Hanspeter Pfister, Jeroen van Baar, and Markus Gross. 2001b. Surface Splatting. In \textit{Proceedings of the 28th Annual Conference on Computer Graphics and Interactive Techniques (SIGGRAPH '01)}. Association for Computing Machinery, New York, NY, USA, 371--378. \url{https://doi.org/10.1145/383259.383300}.
\end{enumerate}
\endgroup
